How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-24 tse-paper/content.tex
bit of brainstorming and corrections

In this section, we survey the emerging field of build log
analysis.
We first start with a differentiation to the related field of general
system log analysis.
Then, we describe the methodology and results of a systematic mapping
study to
determine the state-of-research on build log analysis following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}.

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the analysis of system
logs which are produced during runtime of the system.
The first difference here is that build logs are produced during runtime
of the build of the system, not the system itself.
In terms of the contents of the logs, the main difference is that system
logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level, and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

In principle, one can apply the techniques developed for system log
analysis
to parts of the build logs that have this same structure.
% TODO this explanation is not understandable.
%It needs to better embedded in the surrounding text
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
However, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.
Build logs generally lack this structure and thus require different
bespoke approaches.
% In this article, we focus on extracting a single specified information
% from the build log as a whole with chunk retrieval techniques.
% Chunk
% retrieval techniques are used as a part of log parsing to retrieve the
% values of variable parts in a log message, e.g.\ by using regular
% expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

To guide the data extraction we created a template.
The template form contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''.
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a
pilot study:
both authors extracted data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 46 articles evenly between the two authors
and inspected them as closely as necessary to fill out the template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.
For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.

% TODO: add more concrete example, such as use of retrieved x: developer
%feedback, build data set
Once we had classified all works, we went into the second phase
(``execution phase'') in which we grouped tags
together and found synonyms.

%The full data extraction template and our results of this step can be
%found in our replication package~\cite{brandt2020chunk-replication}.

@@

\subsection{Discussion}
\label{sec:lit-sur:discussion}
% TODO we are extracting failures in the following studies, which is
mainly what
% literature does, too, right? Highlight here and mention later again

@@

@@

% TODO this is not enough for Table 3.
%Where does it come from?
% How did it originate? Also: never single sentence abstracts
\Cref{tab:ctr} shows a comparison of the implemented techniques.

% TODO Somehow, we have to find a better place for this.
%We have been
% using the term 'chunk retrieval' beforehand already -- this
% definition now comes to late.
%The first paragraph should already
% apply to the literature mapping, the second of course only applies
% here.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}
% TODO: could you add two-three more references to the results of RLR in
% the discussion, to show how even seemingly low numbers are much better
% than RLR?

@@

% TODO: these next two sections do not belong under this section --
%they are not a chunk retrieval technique.
%One way to fix it would be to rename the section.
\subsection{Chunk Retrieval Example}
\label{sec:crt-example}

@@

\subsection{Study Process}
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
% TODO passive ...
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of the techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
%of results?
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% This is a weird position for this paragraph
% TODO What is ``this'' referring to? You just defined a bunch of
%equations.
This concludes one execution within our evaluation.
% TODO run vs.
%execution above.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the implemented chunk
retrieval
technique.

@@

% TODO Say something about this being a pecularity of PBE ...
\Cref{fig:failure-reason-PBE} shows the results of chunk
retrieval with PBE.
Out of the overall 400 runs, 5 per each one of the 80 example
sets, PBE extracted all desired lines successfully in 138 cases.
In 59 cases, PBE could synthesize a regular expression program, though
it did not find match on the test build log.
In 30 cases, the synthesized program only extracted a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
% TODO: Perhaps we should call it partially successful? Let's
% discuss this in a meeting
\Cref{lst:pbe-unsuccessful} shows how an example of such
an \emph{unsuccessful retrieval} looks like.
In it, the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize a program consistent with all of the training
examples.

@@

% TODO what about referencing the combined figure at first: something
%like shows the results of CTS on two beanplots of ...
%and ...., and then the subfigure
% TODO this goes for all techniques
\Cref{fig:recall-precision-examplecount-CTS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using CTS for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.

@@

\subsection{Comparison of All Techniques}
%TODO too short
In this section, we aggregate and compare the results from
\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.

% TODO
\Cref{fig:success-partial-all} compares the success of chunk
retrievals differentiated by techniques in our study.
% TODO It shows on the vertical axis the number of ?runs? ...
and on the horizontal ...
CTS and KWS
extract at least some of the desired lines in 79\% and 88.5\%
of the chunk retrieval runs.
With 38.25\%, KWS also has the highest proportion of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.

\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
show the influence of all training and test examples being from the
same structural category compared to being multiple categories
For more
than one category being present, the recall of PBE decreases greatly.
% TODO this is not a meaningful comparsion to RLR.
%One would be to say that
% all of these techniques beat RLR handsdown
For CTS and KWS the values also decrease, while RLR is not affected by
the number of structural categories present.

@@

\subsection{Interpretation of Study Results}
% TODO This is bad style.
%Begin the section by saying what you do in there
% Then at the end, say that you summarized it in Table 3 (or include
%Table 3
% in the discussion throughout the text.)
\Cref{tab:single-technique-recommendations} summarizes the
recommendations which we discuss
in this section.

@@

When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In the study, additional training
examples from the same structural category
did not improve the chunk retrieval.
% Moritz: Why uncomment the following? Is it not true?
% I think it is crucial.
% In fact, unless they
% were in some sense redundant, adding training examples above that even
% hindered the applicability of PBE.
% TODO: it's true.
Though this is because of the structural categories
% which we discuss not in this paragraph but the one above.

@@

\subsection{Recommendation of Suitable Techniques}
% TODO Make intro less generic?
After discussing the three chunk retrieval techniques separately we
now want to unify the results into one recommendation scheme.
% TODO Try to inductiviely let the figure emerge from the text, not this
% ``here is the figure; eat it''.
% C: ``How should I do this?''
% Already a better solution would be at the end of this section: We
% summarized these conditions in the decision tree in Fig ...
\Cref{fig:crt-recommendation} presents a decision tree
to answer the second research question;
If researchers or developers want to retrieve chunks from build logs,
they can follow the decision tree to identify the technique
suited best for their use case.
The decision tree is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.

% shouldn't it also better be in threats to validity?
% it is as well.
%back for my thesis you said we should put it
% directly here to make it more prominent avoid angry critics
% I think it's good here
% but it's also self-contained so feel free to comment it out
\textbf{Caveat!}
This is a preliminary hypothesis based on the results
from our comparison study.
The recommendations could therefore be
influenced by idiosyncrasies of our specific implementation of the
chunk retrieval techniques as well as the \emph{LogChunks}
data set.

@@

\subsection{Using the Recommendation Scheme}
% TODO Perhaps add introduction from recommendation scheme here?

% TODO this is very nice again, perhaps a tiny bit on the trivial side.
% Do reference Figure 17 more, thoguh
To illustrate how one would use the decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

@@

\section{Future Work}
% Actually, this future work is very, *very* good.
%It might be
% the best future work I have ever read in an article.
% One idea would be to sell it as such and tie a bit back to our
% first literature sruvey.
%You can say you give a roadmap to guide
% future research in the field, and sell it in abstract and intro!

@@

\section{Conclusion}
\label{sec:conclusion-fw}
% TODO conclusion should be a bit longer and a little bit more in
% detail.
%Mention general accuracy measures (techniques performed
% up to in F1 score, which is x times better than RLR)
% TODO could also mention future research here: Finally, we gave an
% outline to guide future research efforts in the area of build log
% analysis.
The goal of this paper was to support researchers and developers in
their decision on how to analyze build logs.
To this end, we conducted a systematic mapping study to uncover the
state-of-research on build log analysis.
We implemented three promising chunk retrieval techniques and
compared their performance on the \emph{LogChunks} data set.
Our results show that the structural
representation of the targeted information in the build logs is the
main factor to consider when choosing a suitable technique.
Secondary
factors are the desired confidence into recall and precision of the
produced output and whether precision or recall is more important for
the task at hand.

>>>>

In this section, we survey the emerging field of build log
analysis.
We start with a differentiation to the related field of general
system log analysis.
Then, we describe the methodology and results of a systematic mapping
study to
determine the state-of-research on build log analysis following the
guidelines by Petersen et
al.~\cite{petersen2008systematic,petersen2015guidelines}.

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the analysis of system
logs which are produced during runtime of the system.
The first difference here is that build logs are produced during runtime
of the build of the system, not during runtime of the system itself.
In terms of the contents of the logs, the main difference is that system
logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level, and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

Some of the techniques developed to parse system logs can operate
on build logs as well, such as methods to retrieve the
values of variable parts in a log message, e.g.\ by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.
% This is the easiest example matching here
% amar et al are not in our literature survey
However, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.
Build logs generally lack this structure and thus require different
bespoke approaches.
% if included: this explanation is not understandable.
% It needs to better embedded in the surrounding text
% One example is comparing execution traces to reference
% traces of intended behavior to detect anomalies.
% Amar et
% al.~\cite{amar2019mining} employed a similar approach to detect
% relevant lines in build logs.
% In this article, we focus on extracting a single specified information
% from the build log as a whole with chunk retrieval techniques.
% Chunk
% retrieval techniques are used as a part of log parsing

@@

To guide the data extraction we created a template.
The template form contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''.
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a
pilot study:
both authors extracted data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 46 articles evenly between the two authors
and inspected them as closely as necessary to fill out the template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.
For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.
An example for this is the source of the analyzed build logs,
where we assigned tags such as ``Travis CI'',
``Industrial'', ``Google'', or
``self built''.
Once we had classified all works, we went into the second phase
(``execution phase'') in which we grouped tags
together and found synonyms.
% the following adds to the example but is maybe unneeded / too much
For instance, in the case of the build log source we grouped
``Travis'' and ``travis ci'' together and assigned ``Industrial'' to
all articles that used build logs provided by a company.

The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.

@@

\subsection{Discussion}
\label{sec:lit-sur:discussion}
% TODO we are extracting failures in the following studies, which is
%mainly what
% literature does, too, right? Highlight here and mention later again

@@

% TODO CARO
% start by defining in more detail what a chunk retrieval technique is
% or: characteristics that distinguishe them / to specify them further
% (To Moritz: we have short definitions before, the first time we use
% 'chunk', this is far to detailed to be earlier than here)
% Following that we present each of the techniques in detail.

@@

% TODO CARO this is not enough for Table 3.
%Where does it come from?
% How did it originate? Also: never single sentence abstracts
\Cref{tab:ctr} shows a comparison of the implemented techniques.
% TODO CARO move to end of characteristics section and say that it is
% summary of the techniques along the aspects introducted
% can lead reading / understanding of the future sections

% TODO QUESTION Somehow, we have to find a better place for this.
%We have been
% using the term 'chunk retrieval' beforehand already -- this
% definition now comes to late.
%The first paragraph should already
% apply to the literature mapping, the second of course only applies
% here.

@@

\subsection{Random Line Retrieval (RLR)}
\label{sec:expl-rlr}
% TODO: could you add two-three more references to the results of RLR in
% the discussion, to show how even seemingly low numbers are much better
% than RLR?
% TODO QUESTION: should I add those here? as references to the disc?
% or in the discussion? (you also already added some)
% In general: I think we talk a lot about RLR and it gets wordy.

@@

% TODO: these next two sections do not belong under this section --
%they are not a chunk retrieval technique.
%One way to fix it would be to rename the section.
% TODO QUESTION: Caro show whole structure
% -> introduction to crts, investigated techniques, ???

\subsection{Chunk Retrieval Example}
\label{sec:crt-example}

@@

\subsection{Study Process}
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
We vary its size to measure how many examples we need to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of the techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
%of results?
% motivation why only one test example.
we can also leave that out
% and answer if we are asked about it
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and the oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% This is a weird position for this paragraph
% TODO What is ``this'' referring to? You just defined a bunch of
%equations.
This concludes one run within our evaluation.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the implemented chunk
retrieval
technique.

@@

% TODO Say something about this being a pecularity of PBE ...
\Cref{fig:failure-reason-PBE} shows the results of chunk
retrieval with PBE.
Out of the overall 400 runs, 5 per each one of the 80 example
sets, PBE extracted all desired lines successfully in 138 cases.
In 59 cases, PBE could synthesize a regular expression program, though
it did not find match on the test build log.
In 30 cases, the synthesized program only extracted a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
% TODO: Perhaps we should call it partially successful? Let's
% discuss this in a meeting
% TODO QUESTION: yes we can :)
\Cref{lst:pbe-unsuccessful} shows how an example of such
an \emph{unsuccessful retrieval} looks like.
In it, the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize a program consistent with all of the training
examples.

@@

% TODO what about referencing the combined figure at first: something
%like shows the results of CTS on two beanplots of ...
%and ...., and then the subfigure
% TODO this goes for all techniques
% TODO QUESTION: yes, though then we have more redundant text
% that repeats everywhere and is already in the captions
% -> should we add it for the first time we include a type of figure?
\Cref{fig:recall-precision-examplecount-CTS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using CTS for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.

@@

\subsection{Comparison of All Techniques}
%TODO too short
% TODO CARO give outlook on results here
In this section, we aggregate and compare the results from
\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.

% TODO CARO? check type of graph introduced
\Cref{fig:success-partial-all} compares the success of chunk
retrievals differentiated by techniques in our study.
% TODO It shows on the vertical axis the number of ?runs? ...
% and on the horizontal ...
CTS and KWS
extract at least some of the desired lines in 79\% and 88.5\%
of the chunk retrieval runs.
With 38.25\%, KWS also has the highest proportion of fully
successful extractions, followed by PBE with 34.5\%.
PBE has the
lowest number of partial retrievals with only 18 out of 400 chunk
retrieval runs.

\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
show the influence of all training and test examples being from the
same structural category compared to being multiple categories
For more
than one category being present, the recall of PBE decreases greatly.
% TODO this is not a meaningful comparsion to RLR.
%One would be to say that
% all of these techniques beat RLR handsdown -> discussion!
% TODO QUESTOIN: well they don't in this picture (PBE, multiple sc)
% maybe we can say that one figure earlier?
For CTS and KWS the values also decrease, while RLR is not affected by
the number of structural categories present.

@@

\subsection{Interpretation of Study Results}
% TODO CARO
%Begin the section by saying what you do in there
% Then at the end, say that you summarized it in Table 3 (or include
%Table 3
% in the discussion throughout the text.)
\Cref{tab:single-technique-recommendations} summarizes the
recommendations which we discuss
in this section.

@@

When the training examples are of the same structure, one or two
two training examples are enough input for PROSE to synthesize a regular
expression program with good recall.
In the study, additional training
examples from the same structural category
did not improve the chunk retrieval.
% TODO QUESTION: maybe discuss this
% Moritz: Why uncomment the following? Is it not true?
% I think it is crucial.
% In fact, unless they
% were in some sense redundant, adding training examples above that even
% hindered the applicability of PBE.
% TODO: it's true.
% Though this is because of the structural categories
% which we discuss not in this paragraph but the one above.

@@

\subsection{Recommendation of Suitable Techniques}
% TODO CARO Make intro less generic?
After discussing the three chunk retrieval techniques separately we
now want to unify the results into one recommendation scheme.
% TODO Try to inductiviely let the figure emerge from the text, not this
% ``here is the figure; eat it''.
% C: ``How should I do this?''
% TODO CARO
% Already a better solution would be at the end of this section: We
% summarized these conditions in the decision tree in Fig ...
% also reference to the parts of the figure during the explanation
\Cref{fig:crt-recommendation} presents a decision tree
to answer the second research question;
If researchers or developers want to retrieve chunks from build logs,
they can follow the decision tree to identify the technique
suited best for their use case.
The decision tree is built up of questions
which either lead to more questions or to a leaf node containing a
recommended technique.

% TODO QUESTION
% shouldn't it also better be in threats to validity?
% it is as well.
%back for my thesis you said we should put it
% directly here to make it more prominent avoid angry critics
% I think it's good here
% but it's also self-contained so feel free to comment it out
\textbf{Caveat!}
This is a preliminary hypothesis based on the results
from our comparison study.
The recommendations could therefore be
influenced by idiosyncrasies of our specific implementation of the
chunk retrieval techniques as well as the \emph{LogChunks}
data set.

@@

\subsection{Using the Recommendation Scheme}
% TODO QUESTION: which one do you mean here?
% TODO Perhaps add introduction from recommendation scheme here?

% TODO this is very nice again, perhaps a tiny bit on the trivial side.
% TODO CARO Do reference Figure 17 more, thoguh
To illustrate how one would use the decision tree to find a suitable
chunk retrieval technique we describe two concrete examples: a software
team
wanting to monitor their build performance and a
researcher investigating why builds fail.

@@

\section{Future Work}
% Actually, this future work is very, *very* good.
%It might be
% the best future work I have ever read in an article.
% One idea would be to sell it as such and tie a bit back to our
% first literature survey.
%You can say you give a roadmap to guide
% future research in the field, and sell it in abstract and intro!

@@

\section{Conclusion}
\label{sec:conclusion-fw}
% TODO CARO conclusion should be a bit longer and a little bit more in
% detail.
%Mention general accuracy measures (techniques performed
% up to in F1 score, which is x times better than RLR)
% TODO could also mention future research here: Finally, we gave an
% outline to guide future research efforts in the area of build log
% analysis.
The goal of this paper was to support researchers and developers in
their decision on how to analyze build logs.
To this end, we conducted a systematic mapping study to uncover the
state-of-research on build log analysis.
We implemented three promising chunk retrieval techniques and
compared their performance on the \emph{LogChunks} data set.
Our results show that the structural
representation of the targeted information in the build logs is the
main factor to consider when choosing a suitable technique.
Secondary
factors are the desired confidence into recall and precision of the
produced output and whether precision or recall is more important for
the task at hand.
